Covariate analysis of HBCC RNASeq data reprocessed with STAR-feature counts workflow with Ensembl v75 (ACC and DLPFC with CQN + SVA normlaisation)

### 2018-11-07 code/Rmd/HBCC_DLPFC_STAR_ENSEMBL_v75_CQN_SVA.Rmd
minor changes

knit2synapse::knitToFolderEntity(file = "./HBCC_DLPFC_STAR_ENSEMBL_v75_CQN_SVA.Rmd",
                                 parentId = "syn7501880", #"syn9872607",
                                 entityName = 'HBCC - DLPFC - STAR - FEATURE COUNTS - ENSEMBL v75 - CQN - SVA')
```

@@

```{r synapse.parameters, include=FALSE, cache=TRUE}
parentId = "syn7501880", #'syn9872607';
activityName = 'Covariate adjustments';
activityDescription = 'Covariate analysis of STAR aligned feature counts with Ensembl v75 with CQN and SVA normalisation (DLPFC)';

>>>>

knit2synapse::knitToFolderEntity(file = "./HBCC_DLPFC_STAR_ENSEMBL_v75_CQN_SVA.Rmd",
                                 parentId = 'syn9872607', #"syn7501880", #"syn9872607",
                                 entityName = 'HBCC - DLPFC - STAR - FEATURE COUNTS - ENSEMBL v75 - CQN - SVA')
```

@@

```{r synapse.parameters, include=FALSE, cache=TRUE}
parentId = 'syn9872607'; #"syn7501880"; #
activityName = 'Covariate adjustments';
activityDescription = 'Covariate analysis of STAR aligned feature counts with Ensembl v75 with CQN and SVA normalisation (DLPFC)';
